Chemical potential of liquids and mixtures via Adaptive Resolution Simulation

### 2014-05-07 writeDown/pub.jcp/chem-pot-jcp.tex
add appendix

\def\pd#1#2{\frac{\partial #1}{\partial #2}}
\renewcommand{\vec}[1]{\mbox{\boldmath \small $#1$}}
\newcommand{\concen}{C}
\setlength\parindent{2em} 
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}

@@

\section*{Appendix}
The potential energy function and the force field parameters for all the molecules
were taken from GROMOS53A6 parameter set. Liquid water was described by the SPC
model~\cite{spc}, methanol was described by the model developed by Walser et al~\cite{walser},
urea by the model described in~\cite{urea}, tert-butyl alcohol by the parameter set of~\cite{tba}
and DMSO was described by the model given by Geerke et.al.~\cite{dmso1}. For liquid methanol simulations, 
GROMOS43A1 parameter set was used, as it was shown to be more accurate for calculating excess free energy of 
solvation of methanol in methanol~\cite{vang}.

In all the AdResS simulations, 30 iterations were performed to obtain a 
converged thermodynamic force and a flat density profile. Each iteration consisted 
of 200 ps of equilibration which was followed by 200 ps of data collection. 
The simulations were performed at NVT conditions where the temperature was kept constant 
at 298 K. Simulations of liquid methane and ethane were performed at
111.66 K and 184.52 K respectively. To obtain the chemical potential of coarse-grained component, 
insertion particle method was used, where a trajectory of 8 ns was obtained and the coordinates were written
after every 0.4 ps. \recheck{The insertions of the molecule were performed 4,000,000 times in each 
frame at random locations}. The chemical potential value and
the error were calculated by taking the average and standard deviation of the last ten iterations.

@@

In all the simulations, a leap-frog stochastic dynamics integrator with a time step
of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS~\cite{lincs}
algorithm. In AdResS simulations, it was 
seen that the excess chemical potential values converge after a specific cut-off radius value. Hence, a different 
cut-off radius was used for different simulations in order to obtain a converged value. The full-atom simulations 
were performed using the same cut-off value to have a fair comparison. For liquid water, methanol/water, methane/water, ethane/water
and TBA/water systems, a cut-off radius of 0.9 nm was used for van der Waals and Coulomb interactions, while for rest 
of the systems, a cut-off radius of 1.4 nm was used. Electrostatic 
interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{tba}, 61 for other solutes in SPC
water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.

@@

\bibitem{widom}
B.Widom, J.Chem.Phys.{\bf 39}, 2808 (1963)
\bibitem{ti}
I. G. Tironi and W. F. van Gunsteren, Mol.Phys. {\bf 83}, 381 (1994)
\bibitem{prl12}
S.Fritsch, S.Poblete, C.Junghans, G.Ciccotti, L.Delle Site and K.Kremer, Phys.Rev.Lett. {\bf 108}, 170602 (2012)
\bibitem{jctchan}
H.Wang, C.Sch\"{u}tte and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 2878 (2012)
\bibitem{prx}
H.Wang, C.Hartmann, C.Sch\"{u}tte and L.Delle Site, Phys.Rev.X, {\bf 3}, 011018 (2013)
\bibitem{h-adress}
R.Potestio, S.Fritsch, P.Espanol, R.Delgado-Buscalioni, K.Kremer, R.Everaers, and D.Donadio, Phys.Rev.Lett. {\bf 110}, 108301 (2013)
\bibitem{luigientropy}
L.Delle Site, Entropy {\bf 15} (2013); doi:10.3390
\bibitem{simon-ch}
C.Junghans and S.Poblete, Comp.Phys.Comm. {\bf 181}, 1449 (2010)
\bibitem{nico-debashish}
D. Mukherji, N. F. A. van der Vegt, and K. Kremer, J.Chem.Th.Comp. {\bf 8}, 3536 (2012)
\bibitem{irata}
K.Yoshida, T.Yamaguchi, A.Kovalenko and F.Hirata, J.Phys.Chem.B {\bf 106} 5042 (2002)
\bibitem{florian}
H. Eslami and F. M\"{u}ller-Plathe, J. Comput. Chem. {\bf 28}, 1763 (2007)
\bibitem{vang}
D.P.Geerke, W.F. van Gunsteren, ChemPhysChem, {\bf 7}, 671 (2006)
\bibitem{dmso}
Josefredo R. Pliego Jr and Jose  M. Riveros, Phys. Chem. Chem. Phys., {\bf 4}, 1622 (2002)
\bibitem{urea}
Lorna J. Smith,Herman J. C. Berendsen, and Wilfred F. van Gunsteren, J. Phys. Chem. B, {\bf 108}, 1065 (2004)
\bibitem{nico}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{debashish1}
D.Mukherji, N.F.A.van der Vegt, K.Kremer and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 375 (2012)
\bibitem{gromacs}
http://www.gromacs.org/
\bibitem{spc}
H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans, Reidel, Dordrecht, 331 (1981)
\bibitem{walser}
R. Walser, A. E. Mark, W. F. van Gunsteren, M. Lauterbach, G. Wipff, J. Chem. Phys. {\bf 112}, 10450 (2000)
\bibitem{tba}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{dmso1}
Daan P. Geerke , Chris Oostenbrink , Nico F. A. van der Vegt ,and Wilfred F. van Gunsteren, J. Phys. Chem. B. {\bf 108}, 1436 (2004)
\bibitem{mu}
T. Kristof and G. Rutkai, Chemical Physics Letters. {\bf 445}, 74 (2007). 
\bibitem{mobley}
David L. Mobley, John D. Chodera and Ken A. Dill  J.Chem.Phys. {\bf 125}, 084902 (2006).
\bibitem{bar}
Charles H. Bennett, Journal of Computational Physics {\bf 22}, 245 (1976).
\bibitem{lincs}
Hess, B. and Bekker, H. and Berendsen, H.J.C. and Fraaije, J.G.E.M., Journal of Computational Chemistry {\bf 18}, 1463 (1997).
\bibitem{rf}
I. G. Tironi, R. Sperb, P. E. Smith, W. F. van Gunsteren, J. Chem. Phys. {\bf 102}, 5451 (1995).
\end{thebibliography}

>>>>

\def\pd#1#2{\frac{\partial #1}{\partial #2}}
\renewcommand{\vec}[1]{\mbox{\boldmath \small $#1$}}
\newcommand{\concen}{C}
\setlength\parindent{2em} 
\newcommand{\recheck}[1]{{\color{red} #1}}
\newcommand{\redc}[1]{{\color{red} #1}}            
\newcommand{\vect}[1]{\textbf{\textit{#1}}}
\newcommand{\dof}{{\textrm{DOF}}}
\newcommand{\AT}{{\textrm{{AT}}}}
\newcommand{\EX}{{\textrm{EX}}}
\newcommand{\CG}{{\textrm{CG}}}
\newcommand{\HY}{{\Delta}}
\newcommand{\rdf}{{\textrm{rdf}}}
\newcommand{\thf}{{\textrm{th}}}
\newcommand{\res}{{\textrm{rep}}}
\newcommand{\ext}{{\textrm{extra}}}
\newcommand{\exc}{{\textrm{exc}}}
\newcommand{\thermo}{{\textrm{Q}}}
\newcommand{\hadress}{{\textrm{H}}}
\newcommand{\dadress}{{\textrm{D}}}

@@

\section*{Appendix I}
The potential energy function and the force field parameters for all the molecules
were taken from GROMOS53A6 parameter set. Liquid water was described by the SPC
model~\cite{spc}, methanol was described by the model developed by Walser et al~\cite{walser},
urea by the model described in~\cite{urea}, tert-butyl alcohol by the parameter set of~\cite{tba}
and DMSO was described by the model given by Geerke et.al.~\cite{dmso1}. For liquid methanol simulations, 
GROMOS43A1 parameter set was used, as it was shown to be more accurate for calculating excess free energy of 
solvation of methanol in methanol~\cite{vang}.

In all the AdResS simulations, 30 iterations were performed to obtain a 
converged thermodynamic force and a flat density profile. Each iteration consisted 
of 200 ps of equilibration which was followed by 200 ps of data collection. 
The simulations were performed at NVT conditions where the temperature was kept constant 
at 298 K. Simulations of liquid methane and ethane were performed at
111.66 K and 184.52 K respectively. To obtain the chemical potential of coarse-grained component, 
insertion particle method was used, where a trajectory of 8 ns was obtained and the coordinates were written
after every 0.4 ps. The insertions of the molecule were performed 4,000,000 times in each 
frame at random locations and with random orientations of the molecule. The chemical potential value and
the error were calculated by taking the average and standard deviation of the last ten iterations.

@@

In all the simulations, a leap-frog stochastic dynamics integrator with a time step
of 2 fs and an inverse friction coefficient of 0.1 ps was used. All bond-lengths were constrained using the LINCS 
algorithm. In AdResS simulations, it was 
seen that the excess chemical potential values converge after a specific cut-off radius value. Hence, a different 
cut-off radius was used for different simulations in order to obtain a converged value. The full-atom simulations 
were performed using the same cut-off value to have a fair comparison. For liquid water, methanol/water, methane/water, ethane/water
and TBA/water systems, a cut-off radius of 0.9 nm was used for van der Waals and Coulomb interactions, while for rest 
of the systems, a cut-off radius of 1.4 nm was used. Electrostatic 
interactions beyond the cut-off radius were calculated using the reaction-field term \cite{rf} with a dielectric 
permittivity of 54 for urea in SPC water \cite{urea}, 64.8 for TBA in SPC water \cite{tba}, 61 for other solutes in SPC
water, 19 for methanol and 46 for DMSO as the solvent \cite{vang}.

\section*{Appendix II: The deriviation of the $w_{extra}$}

We consider the potential interpolation of the system:
\begin{align}
  V =
  \sum_{i<j} w(\vect r_i) w(\vect r_j)
  V^\AT_{i,j}
  +
  \sum_{i<j}[1- w(\vect r_i) w(\vect r_j)]
  V^\CG_{i,j},
\end{align}
where  $\vect r_i$ denotes
the center-of-mass (COM) position of the molecule with index $i$.
$V^\AT_{i,j}$ and $V^\CG_{i,j}$ are the atomistic and coarse-grained potential energy between molecule $i$ and $j$, respectively.
Being more precisely, they are
\begin{align}
  V^\AT_{i,j} =
  \sum_{\alpha\in i}\sum_{\beta\in j} V^\AT(\vect r_\alpha - \vect r_\beta),\quad
  V^\CG_{i,j} =
  V^\CG(\vect r_i - \vect r_j).
\end{align}
where index $\alpha$ and $\beta$ denotes the atom position of the corresponding molecule.
The center of mass of the molecule can be calculated by
\begin{align}
  \vect r_i = \sum_{\alpha\in i} \frac{m_\alpha}{\sum_{\alpha\in i} m_\alpha} \vect r_\alpha,
\end{align}
where $m_\alpha$ is the mass of atom $\alpha$.
The
corresponding intermolecular force is given by
\begin{align}\label{eqn:interpol-f}
  \vect F_{i,j} =
  w(\vect r_i) w(\vect r_j)
  \vect F^\AT_{i,j}
  +
  [1- w(\vect r_i) w(\vect r_j)]
  \vect F_{i,j}^\CG
  -
  \nabla w(\vect r_i) w(\vect r_j)
  (V^\AT_{i,j} - V^\CG_{i,j})
\end{align}
We define the force of changing representation:
\begin{align}\label{eqn:frep}
  \vect F_{\res,i} = 
  \sum_j \nabla w(\vect r_i) w(\vect r_j)
  (V^\AT_{i,j} - V^\CG_{i,j})
\end{align}
An important fact is that the force of changing representation is not
symmetric w.r.t molecule $\alpha$ and $\beta$, therefore, the Newton's
action-reaction law (momentum conservation) does not hold anymore for
the potential interpolation approach. On the other hand, the force
interpolation scheme does not preserve
energy, while the potential interpolation
approach has the advantage of energy conservation. In sum, both the
force and potential interpolation approaches do not hold all physical
conservation laws, because the hybrid region is artificially
designed. Therefore, we will take the advantage of both the method and
develop the thermodynamic relation (between the atomistic and
coarse-grained resolutions)  for them at the same time.\\

We use the same notation as in our previous work~\cite{prx}.
The thermodynamic variables for the atomistic and coarse-grained regions
are denoted by $(N_1, V_1, T)$ and $(N_3, V_3, T)$, respectively.
We assume that the hybrid region is an infinitely thin filter that allows
changing of resolution when a molecule passes through it. Therefore, we
reasonably assumes that
\begin{align}
  V &= V_1 + V_3\\
  N &= N_1 + N_3
\end{align}
where $V$ and $N$ are the whole system volume and total number of
molecules in the system, respectively. In this work, we adopt the same
assumptions as those listed in Sec.III.C of Ref.~\cite{prx},
i.e. the system is under the thermodynamic limit, and is short-range
correlated. When the thermodynamic force for both approaches are calculated
(denoted by $\vect F_\thf$ and $\vect F^\hadress_\thf$, respectively.
We use the superscript H to indicate that the thermodynamic force is of the
potential interpolation AdResS),
the flat density profile is enforce to the system:
\begin{align}
  \rho_\HY &= \rho_\AT = \rho_\CG = \rho_0\\
  \rho_\HY^\hadress &= \rho_\AT = \rho_\CG = \rho_0
\end{align}
Where $\rho_0$ is the equilibrium number density of the system defined by $\rho_0 = N/V$.
The thermodynamic force in force interpolation scheme provides the
balance of the grand potential~\cite{prl12}, or equivalently
\begin{align}\label{eqn:peq}
  p_\AT = p_\CG - \rho_0 \,\omega_\thf 
\end{align}
where $p$ denotes the pressure, and $ \omega_\thf$ denotes the
integral of the thermodynamic force. \\

Since the existence of the force of changing representation breaks the
Newton's action-reaction law, the pressure relation between the AT and CG
resolution~\eqref{eqn:peq} does not hold anymore for the potential interpolation,
and should be derived again.
Now assume, for simplicity, the system only changes resolution in $x$ direction.
We impose an infinitesimal increment of the volume $\Delta V$ to the
AT region, and the same decrement of the volume $-\Delta V$ of the CG
region.  The volume of the hybrid region is kept the invariant,
so it is a ``piston''
moves toward the CG region by $\Delta L$,
where we assume $\Delta V = \Delta L\cdot S$, where $S$ is the
cutting surface area.
Here we talk about the infinitely small displacement  $\Delta L$
in the sense that it is even much smaller than the size of the
hybrid region. This is achievable by taking the limit of $\Delta L\rightarrow 0$,
while keeping the system size fixed.
Please also notice the displacement of the molecules are infinitely small,
so one can reasonably assume
the resolution of molecules remains the same under displacement $\Delta L$.
Therefore, the change of the free energy of the system is
\begin{align}\nonumber
  \Delta A \approx&\,
  A_\AT(N_1, V_1+\Delta V, T) -
  A_\AT(N_1, V_1, T)
  +
  A_\CG(N_3, V_3-\Delta V, T) -
  A_\CG(N_3, V_3, T)\\\label{eqn:apptmp3}
  &+
  \int d r\, \rho_0 S\cdot \Delta L\cdot
  \vect F^\hadress_\thf(r)
  -
  \int d r\, \rho_0 S\cdot \Delta L\cdot
  \big\langle \vect F_\res(r)\big\rangle
\end{align}
where $A_\AT$ and $A_\CG$ are the free energy of the AT and CG region, respectively.
$N_1$ and $N_3$ are the number of molecules in the AT and CG region, and
$V_1$ and $V_3$ are the volumn in the AT and CG region, respectively. $T$ is the temperature
of the system.
The last term comes from the work done on the piston. It is composed by
two parts, the fist is the work done by the thermodynamic force, and the
second is due to 
the force of changing representation, which does not vanish due to the break of the Newton's
action-reaction law. The fist and second part of Eq.~\eqref{eqn:interpol-f}
do not contribute, because they obey the Newton's action-reaction law, so
their works cancel as long as the transition region move infinitesimally toward one direction.
The notation $\langle\cdot\rangle$ in Eq.~\eqref{eqn:apptmp3} denotes the ensemble averge.
It is straightforward to show that 
\begin{align}\label{eqn:peq-d}
  \Delta A \approx
  -p_\AT\Delta V + p_\CG\Delta V -
  \rho_0 \Delta V (\omega_\thf^\hadress - \omega_\res), 
\end{align}
where $w_\thf^\hadress$ is the integral of the potential interpolation
thermodynamic force $\vect F_\thf^\hadress$, and
$ \omega_\res$ is the work of changing representation,
which can be explicitly written down as:
\begin{align}\label{eqn:w-rep}
  \omega_\res
  = \int_\HY d r\,\langle \vect F_\res (r)\rangle
  = \int_\HY d r\,\nabla\omega(r)\,
  \big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
\end{align}
The ensemble is taken over all possle positions of the second molecule
in the pairwise interaction. In the case of molecules that contain
more than one atom, the averge is also taken over all possible
conformations of the molecules. 
By using the same argument as the Section III.C of Ref.~\cite{prx}, we can
show that in the thermodynamic limit, the equilibrium volumn of the AT region maxiimize the
free energy, i.e.~$\Delta A / \Delta V
= 0$ that yields
\begin{align}\label{eqn:peq-h}
  p_\CG - p_\AT =  \rho_0 (\omega_\thf^\hadress - \omega_\res).
\end{align}
Comparing with the result of the standard AdResS~Eq.~\eqref{eqn:peq},
we have 
\begin{align}\label{eqn:hd-rel}
  \omega_\res = \omega_\thf^\hadress -   \omega_\thf,
\end{align}
which relates the thermodynamic force of the potential interpolation
and force interpolation AdResS.\\

In Ref.~\cite{prx} we proved that under proper assumptions,
when the flat density profile is enforced by the thermodynamic force,
the chemical potential difference between the different resolutions
is given by
\begin{align}\label{eqn:mueq-d}
 \mu_\CG - \mu_\AT =   \omega_\thf + \omega_\dof + \omega_\ext
\end{align}
where the last term $\omega_\ext$ contributes because the
force interpolation violates the energy conservation of the system.
The same argument can be applied to the potential interpolation approach,
and yields  the chemical potential difference between the AT and CG resolutions
\begin{align}\label{eqn:mueq-h}
 \mu_\CG - \mu_\AT =   \omega^\hadress_\thf + \omega_\dof 
\end{align}
Since we have an auxiliary Hamiltonian by using the the potential
interpolation, we do not have the term $w_\ext$ in the above
fomula.
By comparing~\eqref{eqn:mueq-d} with~\eqref{eqn:mueq-d}, we have the
relation
\begin{align}\label{eqn:hd-rel-2}
  \omega_\thermo^\ext = \omega^\hadress_\thf - \omega_\thf,
\end{align}
which also relates the thermodynamic force of the potential interpolation
and force interpolation AdResS.\\
\\

From Eq.~\eqref{eqn:hd-rel} and \eqref{eqn:hd-rel-2}, we
find the extra work of the thermostat being identical to the work of changing
representation:
\begin{align}\label{eqn:wextra}
  \omega_\ext = \omega_\res,
\end{align}
which basically proves the main conclusion of the paper.  The ensemble
average on the R.H.S.~of Eq.~\eqref{eqn:w-rep} is measured in the
ensemble of the potential interpolation simulation, and the problem is
that whether it is possible to calculate it efficiently in the force
interpolation.  It is obvious that the phase space probability density
of the potential interpolation is consistent with the force
interpolation up to the 1st order (i.e.~density profile, which is
forced to be constant by the thermodynamic force).  It is also
possbile to derive the higher orders of correction, for example, for
the 2nd order property: The radial distribution function~\cite{jctchan}.
However, here we do not consider higher order corrections, because it
has been numerically shown that actually the ensemble average of
$\vect F_\res$ dose not depend on in which ensemble it is
calculated~\cite{prx}. Therefore, we use Eq.~\eqref{eqn:wextra} to
calculate $\omega_\ext$, and measure the ensemble average by the
standard AdResS.  Since in the computer implementation, the CG
molecules also keep the atomistic degrees of freedom eventhough they
are in the CG region, therefore, the kinetic part of $\mu_\AT$ and
$\mu_\CG$ are identical, and $\omega_\dof$ vanishes. Therefore,
by inserting Eq.~\eqref{eqn:wextra} into \eqref{eqn:mueq-d}, we have
\begin{align}
  \mu_\AT^\ext = \mu_\CG^\ext - \int_\HY dr \vect F_\thf(r)
  -\int_\HY dr \nabla\omega(r)\,\big\langle \omega(r')\, [U^\AT(r-r') - U^\CG(r-r')]\big\rangle_{r'}
\end{align}

@@

\bibitem{widom}
B.Widom, J.Chem.Phys.{\bf 39}, 2808 (1963)
\bibitem{ti}
I. G. Tironi and W. F. van Gunsteren, Mol.Phys. {\bf 83}, 381 (1994)
\bibitem{prl12}
S.Fritsch, S.Poblete, C.Junghans, G.Ciccotti, L.Delle Site and K.Kremer, Phys.Rev.Lett. {\bf 108}, 170602 (2012)
\bibitem{jctchan}
H.Wang, C.Sch\"{u}tte and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 2878 (2012)
\bibitem{prx}
H.Wang, C.Hartmann, C.Sch\"{u}tte and L.Delle Site, Phys.Rev.X, {\bf 3}, 011018 (2013)
\bibitem{h-adress}
R.Potestio, S.Fritsch, P.Espanol, R.Delgado-Buscalioni, K.Kremer, R.Everaers, and D.Donadio, Phys.Rev.Lett. {\bf 110}, 108301 (2013)
\bibitem{luigientropy}
L.Delle Site, Entropy {\bf 15} (2013); doi:10.3390
\bibitem{simon-ch}
C.Junghans and S.Poblete, Comp.Phys.Comm. {\bf 181}, 1449 (2010)
\bibitem{nico-debashish}
D. Mukherji, N. F. A. van der Vegt, and K. Kremer, J.Chem.Th.Comp. {\bf 8}, 3536 (2012)
\bibitem{irata}
K.Yoshida, T.Yamaguchi, A.Kovalenko and F.Hirata, J.Phys.Chem.B {\bf 106} 5042 (2002)
\bibitem{florian}
H. Eslami and F. M\"{u}ller-Plathe, J. Comput. Chem. {\bf 28}, 1763 (2007)
\bibitem{vang}
D.P.Geerke, W.F. van Gunsteren, ChemPhysChem, {\bf 7}, 671 (2006)
\bibitem{dmso}
Josefredo R. Pliego Jr and Jose  M. Riveros, Phys. Chem. Chem. Phys., {\bf 4}, 1622 (2002)
\bibitem{urea}
Lorna J. Smith,Herman J. C. Berendsen, and Wilfred F. van Gunsteren, J. Phys. Chem. B, {\bf 108}, 1065 (2004)
\bibitem{nico}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{debashish1}
D.Mukherji, N.F.A.van der Vegt, K.Kremer and L.Delle Site, J.Chem.Th.Comp. {\bf 8}, 375 (2012)
\bibitem{gromacs}
http://www.gromacs.org/
\bibitem{spc}
H. J. C. Berendsen, J. P. M. Postma, W. F. van Gunsteren, J. Hermans, Reidel, Dordrecht, 331 (1981)
\bibitem{walser}
R. Walser, A. E. Mark, W. F. van Gunsteren, M. Lauterbach, G. Wipff, J. Chem. Phys. {\bf 112}, 10450 (2000)
\bibitem{tba}
M.E.Lee and N.F.A. van der Vegt, J.Chem.Phys. {\bf 122}, 114509 (2005)
\bibitem{dmso1}
Daan P. Geerke , Chris Oostenbrink , Nico F. A. van der Vegt ,and Wilfred F. van Gunsteren, J. Phys. Chem. B. {\bf 108}, 1436 (2004)
\bibitem{mu}
T. Kristof and G. Rutkai, Chemical Physics Letters. {\bf 445}, 74 (2007). 
\bibitem{mobley}
David L. Mobley, John D. Chodera and Ken A. Dill  J.Chem.Phys. {\bf 125}, 084902 (2006).
\bibitem{bar}
Charles H. Bennett, Journal of Computational Physics {\bf 22}, 245 (1976).
\bibitem{rf}
I. G. Tironi, R. Sperb, P. E. Smith, W. F. van Gunsteren, J. Chem. Phys. {\bf 102}, 5451 (1995).
\end{thebibliography}
